EagerNet: Early Intrusion Prediction\\in Feed Forward Neural Networks

### 2020-07-14 paper/paper.tex
add content to paper

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%%
%% IMPORTANT NOTICE:
%%
%%% For the copyright see the source file.
%%
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%%
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%%
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.

% Modify this to remove all ACM and conference information (for arXiv for example)
\def\removeHeaders{yes}

\def\tempYes{yes}
\documentclass[9pt,sigconf,letterpaper,dvipsnames\ifx\removeHeaders\tempYes ,nonacm\fi]{acmart}

\copyrightyear{2019}
\acmYear{2019}
\setcopyright{acmcopyright}
\acmConference[Big-DAMA '19]{3rd ACM CoNEXT Workshop on Big DAta, Machine Learning and Artificial Intelligence for Data Communication Networks}{December 9, 2019}{Orlando, FL, USA}
\acmBooktitle{3rd ACM CoNEXT Workshop on Big DAta, Machine Learning and Artificial Intelligence for Data Communication Networks (Big-DAMA '19), December 9, 2019, Orlando, FL, USA}
\acmPrice{15.00}
\acmDOI{10.1145/3359992.3366638}
\acmISBN{978-1-4503-6999-2/19/12}

\usepackage[utf8]{inputenc}

\usepackage{multirow}
\usepackage{blindtext}
\usepackage{soul}
\usepackage[inline]{enumitem}

\usepackage{subfig}

% Acronyms
\usepackage[nomain, toc, acronym]{glossaries}
\glsdisablehyper

\ifx\removeHeaders\tempYes
\settopmatter{printacmref=false} % Removes citation information below abstract
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
\fi

@@

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Eager-Stopping: Early Network Intrusion Prediction\\in Feed Forward Neural Networks}

%% GLOSSARY

@@

@@

\ifx\removeHeaders\tempNo
	\begin{CCSXML}
		<ccs2012>
		<concept>
		<concept_id>10002978.10002997.10002999</concept_id>
		<concept_desc>Security and privacy~Intrusion detection systems</concept_desc>
		<concept_significance>500</concept_significance>
		</concept>
		<concept>
		<concept_id>10010147.10010257.10010293.10003660</concept_id>
		<concept_desc>Computing methodologies~Classification and regression trees</concept_desc>
		<concept_significance>500</concept_significance>
		</concept>
		<concept>
		<concept_id>10010147.10010257.10010293.10010294</concept_id>
		<concept_desc>Computing methodologies~Neural networks</concept_desc>
		<concept_significance>500</concept_significance>
		</concept>
		<concept>
		<concept_id>10003033.10003083.10003014</concept_id>
		<concept_desc>Networks~Network security</concept_desc>
		<concept_significance>300</concept_significance>
		</concept>
		</ccs2012>
	\end{CCSXML}
	\ccsdesc[500]{Security and privacy~Intrusion detection systems}
	\ccsdesc[500]{Computing methodologies~Classification and regression trees}
	\ccsdesc[500]{Computing methodologies~Neural networks}
	\ccsdesc[300]{Networks~Network security}
	\keywords{Network security, Deep Learning, }
\fi

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.

%\author{Maximilian Bachl, Alexander Hartl, Joachim Fabini, Tanja Zseby}
%\affiliation{\institution{Technische Universität Wien}}
%\email{firstname.lastname@tuwien.ac.at}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
%\renewcommand{\shortauthors}{Hartl and Bachl}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
%\begin{abstract}
%  A clear and well-documented \LaTeX\ document is presented as an
%  article formatted for publication by ACM in a conference proceedings
%  or journal publication. Based on the ``acmart'' document class, this
%  article presents and explains many of the common variations, as well
%  as many of the formatting elements an author may use in the
%  preparation of the documentation of their work.
%\end{abstract}
\ifx\removeHeaders\tempYes
	\settopmatter{printfolios=true}
\fi
\maketitle

@@

\subsection{Early Predictions}

\begin{figure*}[htp]

\subfloat[Conventional Feed Forward Neural Network.]{%
  \includegraphics[clip,width=\columnwidth]{figures/ffnn.pdf}%
}
\qquad
\subfloat[Eager-Stopping Neural Network.]{%
  \includegraphics[clip,width=\columnwidth]{figures/eagernet.pdf}%
}

\caption{main caption}

@@

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{subfig}
\usepackage{multirow}
\usepackage{booktabs}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\usepackage[nomain, toc, acronym]{glossaries}
\glsdisablehyper

@@

@@

\begin{document}

\title{EagerNet: Early Intrusion Prediction\\in Feed Forward Neural Networks}

\author{\IEEEauthorblockN{Fares Meghdouri, Maximilian Bachl and Tanja Zseby}
\IEEEauthorblockA{Technische Universität Wien\\
Vienna, Austria\\
firstname.lastname@tuwien.ac.at}}

\maketitle

@@

\begin{IEEEkeywords}

\end{IEEEkeywords}

@@

\subsection{Early Predictions}
\subsubsection{Combined Back-propagation Loss}

\begin{equation}
l = \frac{1}{N} \sum_{n}^{N} -\omega [y_n \cdot \log \sigma (x_{n}) + (1 - y_n) \cdot \log (1 - \sigma (x_{n}))]
\end{equation}

\[
\nabla l = \underbrace{W_{current} \times \nabla l_{current}}_{\text{Current gradient}} + \underbrace{\sum_{i}^{} \nabla l_{i}}_{\text{Next layer gradients}}
\]

\begin{figure*}[htp]
\center
\subfloat[Conventional Feed Forward Neural Network.]{%
  \includegraphics[clip,width=0.45\textwidth]{figures/ffnn_new.pdf}%
}
\\
\subfloat[Eager-Stopping Neural Network: forward-propagation mode.]{%
  \includegraphics[clip,width=0.53\textwidth]{figures/eagernet_new.pdf}%
}
\quad
\subfloat[Eager-Stopping Neural Network: back-propagation mode.]{%
  \includegraphics[clip,width=0.45\textwidth]{figures/eagernet_backprop_new.pdf}%
}

\caption{The difference between conventional neural networks and our proposed architecture.}

@@

\begin{table}

\centering
\begin{tabular}{ccrr}
\toprule
\textbf{Dataset} & \textbf{Architecture} & \textbf{FFNN} & \textbf{EagerNet*}\\
\midrule
\multirow{6}{*}{\rotatebox{90}{CIC-IDS17}} & & & \\
 & & & \\
 & & & \\
 & & & \\
 & & & \\
 & & & \\
\midrule
\multirow{6}{*}{\rotatebox{90}{UNSW-NB15}} & & & \\
 & & & \\
 & & & \\
 & & & \\
 & & & \\
 & & & \\
\midrule
\multirow{6}{*}{\rotatebox{90}{MNIST}} & & & \\
 & & & \\
 & & & \\
 & & & \\
 & & & \\
 & & & \\
\end{tabular}
\vspace{1ex}

{\raggedright * . \par}
\caption{Accuracy scores.}

\begin{figure}[b!]
\includegraphics[width=\columnwidth]{figures/conf_acc_Jul10_15-09-38_gpu_0_3.pdf}
\caption{Accuracy-Confidence plot.\note{red}{FM: this will change}}
\label{fig:pdp_ttl}
\end{figure}

\begin{figure}[b!]
\includegraphics[width=\columnwidth]{figures/acc_multiclass_Jul10_15-18-24_gpu_0_3.pdf}
\caption{Accuracy plot multiclass.\note{red}{FM: this will change}}
\label{fig:pdp_ttl}
\end{figure}
